```{r}
#| results: asis
if (grantee == "All Grantees") {
    summary_text <- "This Data Quality Report examines data collected by all grantees across all of their programs."
} else {
  summary_text <- paste0(
    "This Data Quality Report examines data collected by the **", grantee, "** grantee across the following program(s):\n\n",
    paste0("- ", programs, collapse = "\n")
  )
}

cat(summary_text)
```

During the period from `r format(period_start_date, "%m/%d/%Y")` to `r format(period_end_date, "%m/%d/%Y")` there were **`r nrow(entries_in_period)` enrollments** from **`r dplyr::n_distinct(data_enrollment_client$household_id)` distinct households**. Of these enrollments, **`r n_adults_entry`** were adults and **`r n_hoh_and_or_adult_entry`** were heads of households and/or adults. Additionally, there were **`r nrow(exits_in_period)` exits**, with **`r n_hoh_and_or_adult_exit`** corresponding to heads of households and/or adults.^[Counts for adults and heads of households and/or adults are provided because certain data element responses are only collected for these specific groups.]

Initial Data Quality checks results are shown below:

```{r check-duplicated-enrollment-id}
#| results: asis
n_duplicated_enrollment_ids <- entries_in_period |>
    dplyr::count(enrollment_id) |>
    dplyr::filter(n > 1) |>
    nrow()

n_duplicated_enrollment_ids_string <- ifelse(
    n_duplicated_enrollment_ids == 0,
    "✅ There are no duplicated enrollment IDs.",
    paste0("❌ There are ", n_duplicated_enrollment_ids, " duplicated enrollment IDs.")
)

cat(n_duplicated_enrollment_ids_string)
```

```{r check-one-head-of-household-per-household}
#| results: asis
distinct_n_hoh_per_h <- data_enrollment_client |>
    dplyr::summarise(
        n_hoh = sum(relationship_to_ho_h == "Self (head of household)"),
        .by = "household_id"
    ) |>
    dplyr::count(n_hoh) |>
    dplyr::pull(n_hoh)

if (length(distinct_n_hoh_per_h) == 1 && distinct_n_hoh_per_h == 1) {
    cat("✅ All households have exactly one head of household.")
} else {
    if (0 %in% distinct_n_hoh_per_h) {
        cat("❌ Some households are missing a head of household.")
    }
    if (any(distinct_n_hoh_per_h > 1)) {
        cat("❌ Some households have more than one head of household.")
    }
}
```

```{r check-exit-associated-with-enrollment}
#| results: asis
n_exits_without_an_enrollment_record <- exits_in_period |>
    dplyr::anti_join(
        y = dm$enrollment,
        by = c("enrollment_id", "personal_id", "organization_id")
    ) |>
    nrow()

if (n_exits_without_an_enrollment_record == 0) {
    cat("✅ All exits are associated with an enrollment.")
} else {
    cat(glue::glue("❌ { n_exits_without_an_enrollment_record } aren't associated with an enrollment."))
}
```
