---
title: Data Quality Report
subtitle: "`r paste('Period:', params$period_start_date, 'to', params$period_end_date)`"
subsubtitle: "`r params$grantee$name`"
execute:
  echo: false
params:
  period_start_date: "2025-07-01"
  period_end_date: "2025-09-30"
  grantee: NULL
---

```{r set-default-params-for-interactive-development}
# Set default params for interactive development
if (!exists("params")) {
    params <- list(
        period_start_date = lubridate::ymd("2025-07-01"),
        period_end_date = lubridate::ymd("2025-09-30")
    )
}
```

```{r make-params-available-to-included-documents}
# Make params available to included documents
period_start_date <- lubridate::ymd(params$period_start_date)
period_end_date <- lubridate::ymd(params$period_end_date)
grantee <- params$grantee$name
programs <- params$grantee$programs
```

```{r load-data-and-utils}
purrr::walk(
  .x = list.files("R", full.names = TRUE),
  .f = source
)
```

## Overview

### Introduction

{{< include qmd/_01_01_introduction.qmd >}}

### Responses Summary

{{< include qmd/_01_02_responses_summary.qmd >}}

## Data Elements Analysis

### Introduction

{{< include qmd/_02_01_introduction.qmd >}}

### Universal Data Elements

#### Social Security Number

SSN data is recorded in two fields:

- Social Security Number
- SSN Data Quality

The following table cross-references the values reported in the SSN Data Quality field with the actual number of digits recorded in the SSN field:

```{r check-ssn-responses}
data_enrollment_client |>
    create_data_quality_table(
        response_column = "ssn_data_quality",
        combine_responses = FALSE,
        response_values = c("Full SSN reported", "Approximate or partial SSN reported"),
        group_column = "ssn_length",
        group_column_label = "SSN Length",
        table_title = "SSN Data Quality and SSN Length"
    ) |>
    gt::cols_width(
        data_quality_status ~ gt::pct(49),
        gt::everything() ~ gt::pct(17)
    )
```

#### Date of Birth

This section analyzes client age, which is calculated at project start based on date of birth.

```{r check-age-range}
#| results: asis
min_age <- min(data_enrollment_client$age, na.rm = TRUE)
max_age <- max(data_enrollment_client$age, na.rm = TRUE)

cat(paste0("Clients reported ages ranging from ", min_age, " to ", max_age, " years."))
```

```{r check-missing-age}
#| results: asis
n_missing_age <- data_enrollment_client |>
    dplyr::filter(age_grouped == "Data not collected") |>
    nrow()

n_missing_age_string <- ifelse(
    n_missing_age == 0,
    "✅ All clients reported an age value.",
    paste0("⚠️ ", n_missing_age, " client", ifelse(n_missing_age > 1, "s", ""), " reported no age value.")
)

cat(n_missing_age_string)
```

The following chart shows the distribution of clients by age:

```{r check-age-distribution}
if (nrow(data_enrollment_client) > 0) {
    data_enrollment_client |>
        ggplot2::ggplot() +
        ggplot2::geom_histogram(
            mapping = ggplot2::aes(x = age),
            binwidth = 3,
            boundary = 0,
            closed = "left",
            fill = palette$light_blue,
            color = palette$navy_blue
        ) +
        ggplot2::scale_x_continuous(
            breaks = seq(
                floor(min(min_age, 0) / 3) * 3,
                ceiling(max_age / 3) * 3,
                3
            )
        ) +
        ggplot2::scale_y_continuous(
            expand = ggplot2::expansion(mult = c(0, 0.15))
        ) +
        ggplot2::labs(
            title = "Clients by Age",
            x = "Age (Years)",
            y = "Count"
        ) +
        ggplot2::theme_bw()
}
```

#### Race and Ethnicity

Clients can self-identificate with one or more different racial and/or ethnic categories. This data element is collected at record creation and is required for all clients.

The following table shows the distribution of clients based on how many race/ethnicity identities they selected:

```{r process-ethnicity-data}
ethnicity_summary <- dm$ethnicity |>
    dplyr::semi_join(
        y = entries_in_period,
        by = c("personal_id", "organization_id")
    ) |>
    dplyr::summarise(
        n_ethnicities = sum(ethnicity != "Data not collected"),
        n_missing = sum(ethnicity == "Data not collected"),
        .by = c("personal_id", "organization_id")
    )

data_ethnicity <- entries_in_period |>
    dplyr::left_join(
        y = ethnicity_summary,
        by = c("personal_id", "organization_id")
    )
```

```{r check-etchnicity-count}
data_ethnicity_summary <- data_ethnicity |>
    dplyr::count(n_ethnicities) |>
    janitor::adorn_totals(where = "row", name = "Total Enrollments")

data_ethnicity_summary |>
    gt::gt() |>
    gt::tab_header(
        title = "Client Self-Identified Race/Ethnicity Selections"
    ) |>
    gt::cols_label(
        n_ethnicities = "Number of Identities Selected",
        n = "Count"
    ) |>
    gt::cols_align(
        align = "left",
        columns = n_ethnicities
    ) |>
    gt::cols_width(
        n_ethnicities ~ gt::pct(70),
        gt::everything() ~ gt::pct(25)
    ) |>
    gt::tab_options(
        table.font.names = "Roboto",
        column_labels.font.weight = "bold"
    ) |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_body(rows = nrow(data_ethnicity_summary))
    )
```

```{r check-correct-missing}
#| results: asis
problematic_records <- data_ethnicity |>
    dplyr::filter(n_missing == 1, n_ethnicities > 0)

n_problematic <- nrow(problematic_records)

if (n_problematic == 0) {
    cat("✅ No records have missing alongside other valid ethnicity values.")
} else {
    cat(paste0("❌ ", n_problematic, " records have missing alongside other valid ethnicity values."))
}
```

#### Veteran Status

This data element is collected at record creation and is required for all adults.

```{r check-veteran-status-responses}
data_enrollment_client |>
    dplyr::filter(is_adult == "Yes") |>
    create_data_quality_table(
        response_column = "veteran_status",
        total_label = "Total Adult Enrollments",
        table_title = "Veteran Status"
    )
```

#### Relationship to Head of Household

This data element is collected at project start and is required for all clients.
```{r check-relationship-to-head-of-household-responses}
data_enrollment_client |>
    create_data_quality_table(
        response_column = "relationship_to_ho_h",
        total_label = "Total Enrollments",
        no_response_values = "Data not collected",
        table_title = "Relationship to Head of Household"
    )
```

The following chart shows the distribution of heads of household by age group:

```{r check-heads-of-household-age}
data_enrollment_client |>
    dplyr::filter(relationship_to_ho_h == "Self (head of household)") |>
    dplyr::count(age_grouped, .drop = FALSE) |>
    ggplot2::ggplot() +
    ggplot2::geom_bar(
        mapping = ggplot2::aes(
            x = age_grouped,
            y = n
        ),
        stat = "identity",
        fill = palette$light_blue,
        color = palette$navy_blue
    ) +
    ggplot2::geom_text(
        mapping = ggplot2::aes(
            x = age_grouped,
            y = n,
            label = ifelse(n == 0, "", n)
        ),
        hjust = -0.2
    ) +
    ggplot2::coord_flip() +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(mult = c(0, 0.15))) +
    ggplot2::labs(
        title = "Heads of Household by Age",
        x = "Age (Years)",
        y = "Head of Household Count"
    ) +
    ggplot2::theme_bw()

```

#### Living Situation

This data element is collected at project start for heads of household and/or adults and at project exit for all clients.

```{r check-living-situation-responses-entry}
data_enrollment_client |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "living_situation",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Living Situation (Entry)"
    )
```

```{r check-living-situation-responses-exit}
data_exit |>
    create_data_quality_table(
        response_column = "destination",
        total_label = "Total Exits",
        table_title = "Living Situation (Exit)"
    )
```

### Program Specific Data Elements

This section analyses data stored in the following files:

- `Enrollment.csv`
- `Exit.csv`
- `Disabilities.csv`
- `EmploymentEducation.csv`
- `HealthAndDV.csv`
- `IncomeBenefits.csv`

Throughout the section, `Disabilities.csv`, `EmploymentEducation.csv`, `HealthAndDV.csv` and `IncomeBenefits.csv` are collectively referred to as *program-specific data files*.

Data records in program-specific data files that are generated at project start must match an Enrollment ID in `Enrollment.csv`. In addition, all Enrollments ID in `Enrollment.csv` must have a match in each program-specific data file.

Similarly, data records in program-specific data files that are generated at project exit must match an Enrollment ID in `Exit.csv` and all Enrollments ID in `Exit.csv` must have a match in each program-specific data file.

Sometimes, data records are missing from program-specific data files (i.e. an Enrollment ID that exists in `Enrollment.csv` or `Exit.csv` doesn't exist in a program-specific data file). For that reason, each subsection below that analyses a data element stored in a program-specific data file starts with a data record match check.

The following definitions clarify the terminology used in data record match checks:

- **A data record collected at entry that matches an enrollment record** is a data record in a program-specific data file with an Enrollment ID that exists in `Enrollment.csv`. **All data records collected at entry match an enrollment record** when each Enrollment ID in the program-specific data file exists in `Enrollment.csv`. **A data record collected at entry doesn't match an enrollment record** when the data record has an Enrollment ID that doesn't exist in `Enrollment.csv`.

- **An enrollment that has a data record** is an enrollment record in `Enrollment.csv` with an Enrollment ID that exists in the program-specific data file. **All enrollments have a data record** when each Enrollment ID in `Enrollment.csv` exists in the program-specific data file. **An enrollment is missing a data record** when the Enrollment ID in `Enrollment.csv` doesn't exist in the program-specific data file.

- **A data record collected at exit that matches an exit record** is a data record in a program-specific data file with an Enrollment ID that exists in `Exit.csv`. **All data records collected at exit match an exit record** when each Enrollment ID in the program-specific data file exists in `Exit.csv`. **A data record collected at exit doesn't match an exit record** when the data record has an Enrollment ID that doesn't exist in `Exit.csv`.

- **An exit that has a data record** is an exit record in `Exit.csv` with an Enrollment ID that exists in the program-specific data file. **All exits have a data record** when each Enrollment ID in `Exit.csv` exists in the program-specific data file. **An exit is missing a data record** when the Enrollment ID in `Exit.csv` doesn't exist in the program-specific data file.

Finally, it is important to note that missing records affect the enrollment and exit totals shown in the tables below, which may differ from the overall totals reported in the overview section.

#### Common Program Specific Data Elements

##### Income, Benefits and Insurance

Data record match check results for income, benefits and insurance data records in `IncomeBenefits.csv` are shown below:

```{r check-income-sources-record-match}
#| results: asis
check_record_match(
    data_entry = data_income_entry,
    entries = entries_in_period,
    data_exit = data_income_exit,
    exits = exits_in_period
)
```

###### Income and Sources

This data element is collected at project start and project exit and is required for heads of household and/or adults only.

####### Entry

```{r check-income-responses-entry}
data_income_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "income_from_any_source",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Income from Any Source (Entry)"
    )
```

The following additional checks were performed:

```{r check-income-detail-responses-entry}
data_detail_income_entry |>
    dplyr::count(
        is_hoh_and_or_adult,
        any_source_response_grouped,
        has_total_monthly_income,
        selected_one_or_more_sources
    ) |>
    gt::gt() |>
    gt::tab_header(
        title = "Detailed Income Analysis (Entry)"
    ) |>
    gt::cols_label(
        is_hoh_and_or_adult = "HoH and / or Adult",
        any_source_response_grouped = "Income from Any Source",
        has_total_monthly_income = "Reported Value",
        selected_one_or_more_sources = "Selected one or more Sources",
        n = "Count"
    ) |>
    gt::tab_options(
        table.font.names = "Roboto"
    )
```

####### Exit

```{r check-income-responses-exit}
data_income_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "income_from_any_source",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Income from Any Source (Exit)"
    )
```

The following additional checks were performed:

```{r check-income-detail-responses-exit}
data_detail_income_exit |>
    dplyr::count(
        is_hoh_and_or_adult,
        any_source_response_grouped,
        has_total_monthly_income,
        selected_one_or_more_sources
    ) |>
    gt::gt() |>
    gt::tab_header(
        title = "Detailed Income Analysis (Exit)"
    ) |>
    gt::cols_label(
        is_hoh_and_or_adult = "HoH and / or Adult",
        any_source_response_grouped = "Income from Any Source",
        has_total_monthly_income = "Reported Value",
        selected_one_or_more_sources = "Selected one or more Sources",
        n = "Count"
    ) |>
    gt::tab_options(
        table.font.names = "Roboto"
    )
```

###### Non-Cash Benefits

This data element is collected at project start and project exit and is required for heads of household and/or adults only.

####### Entry

```{r check-benefits-responses-entry}
data_benefits_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "benefits_from_any_source",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Benefits from Any Source (Entry)"
    )
```

The following additional checks were performed:

```{r check-benefits-detail-responses-entry}
data_detail_benefits_entry |>
    dplyr::count(
        is_hoh_and_or_adult,
        any_source_response_grouped,
        selected_one_or_more_sources
    ) |>
    gt::gt() |>
    gt::tab_header(
        title = "Detailed Benefits Analysis (Entry)"
    ) |>
    gt::cols_label(
        is_hoh_and_or_adult = "HoH and / or Adult",
        any_source_response_grouped = "Benefits from Any Source",
        selected_one_or_more_sources = "Selected one or more Sources",
        n = "Count"
    ) |>
    gt::tab_options(
        table.font.names = "Roboto"
    )
```

####### Exit

```{r check-benefits-responses-exit}
data_benefits_exit |>
    create_data_quality_table(
        response_column = "benefits_from_any_source",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Benefits from Any Source (Exit)"
    )
```

The following additional checks were performed:

```{r check-benefits-detail-responses-exit}
data_detail_benefits_exit |>
    dplyr::count(
        is_hoh_and_or_adult,
        any_source_response_grouped,
        selected_one_or_more_sources
    ) |>
    gt::gt() |>
    gt::tab_header(
        title = "Detailed Benefits Analysis (Exit)"
    ) |>
    gt::cols_label(
        is_hoh_and_or_adult = "HoH and / or Adult",
        any_source_response_grouped = "Benefits from Any Source",
        selected_one_or_more_sources = "Selected one or more Sources",
        n = "Count"
    ) |>
    gt::tab_options(
        table.font.names = "Roboto"
    )
```

###### Health Insurance

This data element is collected at project start and project exit and is required for all clients.

####### Entry

```{r check-health-insurance-responses-entry}
data_health_insurance_entry |>
    create_data_quality_table(
        response_column = "insurance_from_any_source",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Enrollments",
        table_title = "Insurance from Any Source (Entry)"
    )
```

The following additional checks were performed:

```{r check-health-insurance-detail-responses-entry}
data_detail_health_insurance_entry |>
    dplyr::count(
        any_source_response_grouped,
        selected_one_or_more_sources
    ) |>
    gt::gt() |>
    gt::tab_header(
        title = "Detailed Heath Insurance Analysis (Entry)"
    ) |>
    gt::cols_label(
        any_source_response_grouped = "Insurance from Any Source",
        selected_one_or_more_sources = "Selected one or more Sources",
        n = "Count"
    ) |>
    gt::tab_options(
        table.font.names = "Roboto"
    )
```

####### Exit

```{r check-health-insurance-responses-exit}
data_health_insurance_exit |>
    create_data_quality_table(
        response_column = "insurance_from_any_source",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Exits",
        table_title = "Insurance from Any Source (Exit)"
    )
```

The following additional checks were performed:

```{r check-health-insurance-detail-responses-exit}
data_detail_health_insurance_exit |>
    dplyr::count(
        any_source_response_grouped,
        selected_one_or_more_sources
    ) |>
    gt::gt() |>
    gt::tab_header(
        title = "Detailed Health Insurance Analysis (Exit)"
    ) |>
    gt::cols_label(
        any_source_response_grouped = "Insurance from Any Source",
        selected_one_or_more_sources = "Selected one or more Sources",
        n = "Count"
    ) |>
    gt::tab_options(
        table.font.names = "Roboto"
    )
```

##### Health Conditions and Disabilities

Data elements in this section are collected at project start and project exit and are required for all clients.

Data record match check results for health conditions and disabilities data records in `Disabilities.csv` are shown below:

```{r check-health-conditions-disabilites-record-match}
#| results: asis
check_record_match(
    data_entry = data_health_conditions_and_disabilites_entry,
    entries = entries_in_period,
    data_exit = data_health_conditions_and_disabilites_exit,
    exits = exits_in_period
)
```

###### Physical Disability

```{r check-physical-disability-responses-entry}
data_health_conditions_and_disabilites_entry |>
    dplyr::filter(disability_type == "Physical Disability") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Enrollments",
        table_title = "Physical Disability (Entry)"
    )
```

```{r check-physical-disability-responses-exit}
data_health_conditions_and_disabilites_exit |>
    dplyr::filter(disability_type == "Physical Disability") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Exits",
        table_title = "Physical Disability (Exit)"
    )
```

###### Developmental Disability

```{r check-developmental-disability-responses-entry}
data_health_conditions_and_disabilites_entry |>
    dplyr::filter(disability_type == "Developmental Disability") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Enrollments",
        table_title = "Developmental Disability (Entry)"
    )
```

```{r check-developmental-disability-responses-exit}
data_health_conditions_and_disabilites_exit |>
    dplyr::filter(disability_type == "Developmental Disability") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Exits",
        table_title = "Developmental Disability (Exit)"
    )
```

###### Chronic Health Condition

```{r check-chronic-health-condition-responses-entry}
data_health_conditions_and_disabilites_entry |>
    dplyr::filter(disability_type == "Chronic Health Condition") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Enrollments",
        table_title = "Chronic Health Condition (Entry)"
    )
```

```{r check-chronic-health-condition-responses-exit}
data_health_conditions_and_disabilites_exit |>
    dplyr::filter(disability_type == "Chronic Health Condition") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Exits",
        table_title = "Chronic Health Condition (Exit)"
    )
```

###### HIV/AIDS

```{r check-hiv-aids-responses-entry}
data_health_conditions_and_disabilites_entry |>
    dplyr::filter(disability_type == "HIV/AIDS") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Enrollments",
        table_title = "HIV/AIDS (Entry)"
    )
```

```{r check-hiv-aids-responses-exit}
data_health_conditions_and_disabilites_exit |>
    dplyr::filter(disability_type == "HIV/AIDS") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Exits",
        table_title = "HIV/AIDS (Exit)"
    )
```
###### Mental Health Disorder

```{r check-mental-health-disorder-responses-entry}
data_health_conditions_and_disabilites_entry |>
    dplyr::filter(disability_type == "Mental Health Disorder") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Enrollments",
        table_title = "Mental Health Disorder (Entry)"
    )
```

```{r check-mental-health-disorder-responses-exit}
data_health_conditions_and_disabilites_exit |>
    dplyr::filter(disability_type == "Mental Health Disorder") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Exits",
        table_title = "Mental Health Disorder (Exit)"
    )
```

###### Substance Use Disorder

```{r check-substance-use-disorder-responses-entry}
data_health_conditions_and_disabilites_entry |>
    dplyr::filter(disability_type == "Substance Use Disorder") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Enrollments",
        table_title = "Substance Use Disorder (Entry)"
    )
```

```{r check-substance-use-disorder-responses-exit}
data_health_conditions_and_disabilites_exit |>
    dplyr::filter(disability_type == "Substance Use Disorder") |>
    create_data_quality_table(
        response_column = "disability_response",
        total_label = "Total Exits",
        table_title = "Substance Use Disorder (Exit)"
    )
```

##### Domestic Violence

This data element is collected at project start and is required for heads of household and/or adults only.

Data record match check results for domestic violence data records in `HealthAndDV.csv` are shown below:

```{r check-domestic-violence-record-match}
#| results: asis
check_record_match(
    data_entry = data_domestic_violence_entry,
    entries = entries_in_period
)
```

```{r check-domestic-violence-responses-entry}
data_domestic_violence_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "domestic_violence_survivor",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Domestic Violence Survivor (Entry)"
    )
```

The following tables focus on responses from domestic violence survivors:

```{r check-when-occurred-responses-entry}
data_domestic_violence_entry |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        domestic_violence_survivor == "Yes"
    ) |>
    create_data_quality_table(
        response_column = "when_occurred",
        total_label = "Total Domestic Violence Survivors",
        table_title = "When Occurred (Entry)"
    )
```

```{r check-currently-fleeing-responses-entry}
data_domestic_violence_entry |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        domestic_violence_survivor == "Yes"
    ) |>
    create_data_quality_table(
        response_column = "currently_fleeing",
        total_label = "Total Domestic Violence Survivors",
        table_title = "Currently Fleeing (Entry)"
    )
```

#### Federal Partner Program Specific Data Elements

##### RHY

###### Referral Source

This data element is collected at project start and is required for heads of household and/or adults only.

```{r check-referral-source-responses}
data_enrollment_client |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "referral_source",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Referral Source"
    )
```

###### Education

This data element is collected at project start and project exit and is required for heads of household and/or adults only.

Data record match check results for education data records in `EmploymentEducation.csv` are shown below:

```{r check-education-record-match}
#| results: asis
check_record_match(
    data_entry = data_education_entry,
    entries = entries_in_period,
    data_exit = data_education_exit,
    exits = exits_in_period
)
```

####### Last Grade Completed

```{r check-last-grade-completed-responses-entry}
data_education_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "last_grade_completed",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Last Grade Completed (Entry)"
    )
```

```{r check-last-grade-completed-responses-exit}
data_education_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "last_grade_completed",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Last Grade Completed (Exit)"
    )
```

####### School Status

```{r check-school-status-responses-entry}
data_education_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "school_status",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "School Status (Entry)"
    )
```

```{r check-school-status-responses-exit}
data_education_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "school_status",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "School Status (Exit)"
    )
```

###### Employment Status

This data element is collected at project start and project exit and is required for heads of household and/or adults only.

Data record match check results for employment data records in `EmploymentEducation.csv` are shown below:

```{r check-employment-record-match}
#| results: asis
check_record_match(
    data_entry = data_employment_entry,
    entries = entries_in_period,
    data_exit = data_employment_exit,
    exits = exits_in_period
)
```

####### Entry

```{r check-employed-responses-entry}
data_employment_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "employed",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Employment Status (Entry)"
    )
```

The following table focus on responses from employed heads of household and/or adults:

```{r check-employment-type-responses-entry}
data_employment_entry |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        employed == "Yes"
    ) |>
    create_data_quality_table(
        response_column = "employment_type",
        no_response_values = "Data not collected",
        total_label = "Total Employed Heads of Household and/or Adults",
        table_title = "Employment Type (Entry)"
    )
```

The following table focus on responses from unemployed heads of household and/or adults:

```{r check-not-employed-reason-responses-entry}
data_employment_entry |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        employed == "No"
    ) |>
    create_data_quality_table(
        response_column = "not_employed_reason",
        no_response_values = "Data not collected",
        total_label = "Total Unemployed Heads of Household and/or Adults",
        table_title = "Not Employed Reason (Entry)"
    )
```

####### Exit

```{r check-employed-responses-exit}
data_employment_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "employed",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Employment Status (Exit)"
    )
```

The following table focus on responses from employed heads of household and/or adults:

```{r check-employment-type-responses-exit}
data_employment_exit |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        employed == "Yes"
    ) |>
    create_data_quality_table(
        response_column = "employment_type",
        no_response_values = "Data not collected",
        total_label = "Total Employed Heads of Household and/or Adults",
        table_title = "Employment Type (Exit)"
    )
```

The following table focus on responses from unemployed heads of household and/or adults:

```{r check-not-employed-reason-responses-exit}
data_employment_exit |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        employed == "No"
    ) |>
    create_data_quality_table(
        response_column = "not_employed_reason",
        no_response_values = "Data not collected",
        total_label = "Total Unemployed Heads of Household and/or Adults",
        table_title = "Not Employed Reason (Exit)"
    )
```

###### Health Status

Data elements in this section are collected at project start and project exit and are required for heads of household and/or adults only.

Data record match check results for health status data records in `HealthAndDV.csv` are shown below:

```{r check-health-status-record-match}
#| results: asis
check_record_match(
    data_entry = data_health_entry,
    entries = entries_in_period,
    data_exit = data_health_exit,
    exits = exits_in_period
)
```

####### General Health Status

```{r check-general-health-responses-entry}
data_health_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "general_health_status",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "General Health Status (Entry)"
    )
```

```{r check-general-health-responses-exit}
data_health_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "general_health_status",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "General Health Status (Exit)"
    )
```

####### Dental Health Status

```{r check-dental-health-responses-entry}
data_health_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "dental_health_status",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Dental Health Status (Entry)"
    )
```

```{r check-dental-health-responses-exit}
data_health_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "dental_health_status",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Dental Health Status (Exit)"
    )
```

####### Mental Health Status

```{r check-mental-health-responses-entry}
data_health_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "mental_health_status",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Mental Health Status (Entry)"
    )
```

```{r check-mental-health-responses-exit}
data_health_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "mental_health_status",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Mental Health Status (Exit)"
    )
```

####### Pregnancy Status

```{r check-pregnancy-responses-entry}
data_health_entry |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "pregnancy_status",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Pregnancy Status (Entry)"
    )
```

```{r check-pregnancy-responses-exit}
data_health_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "pregnancy_status",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Pregnancy Status (Exit)"
    )
```

###### Formerly a Ward of Child Welfare/Foster Care Agency

This data element is collected at project start and is required for heads of household and/or adults only.

```{r check-formerly-ward-of-child-welfare-foster-care-agency}
data_enrollment_client |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "former_ward_child_welfare",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Formerly a Ward of Child Welfare/Foster Care Agency"
    )
```

###### Formerly a Ward of Juvenile Justice System

This data element is collected at project start and is required for heads of household and/or adults only.

```{r check-formerly-ward-of-juvenile-justice-system}
data_enrollment_client |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "former_ward_juvenile_justice",
        total_label = "Total Heads of Household and/or Adults Enrollments",
        table_title = "Formerly a Ward of Juvenile Justice System"
    )
```

###### Commercial Sexual Exploitation / Sex Trafficking

This data element is collected at project exit and is required for heads of household and/or adults only.

```{r check-exchange-for-sex-responses}
data_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "exchange_for_sex",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Exchange for Sex (Exit)"
    )
```

The following tables focus on heads of household and/or adults that received anything in exchange for sex:

```{r check-count-exchange-for-sex-responses}
data_exit |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        exchange_for_sex == "Yes"
    ) |>
    create_data_quality_table(
        response_column = "count_of_exchange_for_sex",
        total_label = "Total Heads of Household and/or Adults that Exchanged for Sex",
        table_title = "Count Exchange for Sex (Exit)"
    )
```

```{r check-asked-or-forced-to-exchange-for-sex-responses}
data_exit |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        exchange_for_sex == "Yes"
    ) |>
    create_data_quality_table(
        response_column = "asked_or_forced_to_exchange_for_sex",
        total_label = "Total Heads of Household and/or Adults that Exchanged for Sex",
        table_title = "Asked or Forced to Exchange for Sex (Exit)"
    )
```

###### Labor Exploitation / Trafficking

This data element is collected at project exit and is required for heads of household and/or adults only.

```{r check-workplace-violence-threats-promise-difference-responses-hoh-adults}
data_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    dplyr::mutate(
        workplace_promise_difference = factor(
            workplace_promise_difference,
            levels = c(
                "Yes",
                "No",
                "Client doesn't know",
                "Client prefers not to answer",
                "Data not collected"
            )
        )
    ) |>
    create_data_quality_table(
        response_column = "work_place_violence_threats",
        response_column_label = "Workplace Violence Threats",
        combine_responses = FALSE,
        response_values = c("Yes", "No"),
        group_column = "workplace_promise_difference",
        group_column_label = "Workplace Promise Difference",
        table_title = "Workplace Violence Threats / Promise Difference (Exit)"
    ) |>
    gt::tab_style(
        style = gt::cell_text(weight = "bold"),
        locations = gt::cells_body(columns = 1)
    ) |>
    gt::cols_width(
        data_quality_status ~ gt::pct(35),
        `Data not collected` ~ gt::pct(12),
        `Client prefers not to answer` ~ gt::pct(17),
        `Client doesn't know` ~ gt::pct(17),
        `Yes` ~ gt::pct(8),
        `No` ~ gt::pct(8)
    )
```

The following table focus on heads of household and/or adults that experienced workplace violence and/or promise difference:

```{r check-coerced-to-continue-work-responses}
data_exit |>
    dplyr::filter(
        is_hoh_and_or_adult == "Yes",
        work_place_violence_threats == "Yes" | workplace_promise_difference == "Yes"
    ) |>
    create_data_quality_table(
        response_column = "coerced_to_continue_work",
        total_label = "Total Heads of Household and/or Adults that Experienced Workplace Violence and/or Promise Difference",
        table_title = "Coerced to Continue Work (Exit)"
    )
```

###### Project Completion Status

This data element is collected at project exit and is required for heads of household and/or adults only.

```{r check-project-completion-status-responses}
data_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "project_completion_status",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Project Completion Status (Exit)"
    )
```

###### Counseling

This data element is collected at project exit and is required for heads of household and/or adults only.

```{r check-counseling-responses}
data_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "counseling_received",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Counseling (Exit)"
    )
```

###### Safe and Appropriate Exit

This data element is collected at project exit and is required for heads of household and/or adults only.

```{r check-destination-safe-client-responses}
data_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "destination_safe_client",
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Destination Safe Client (Exit)"
    )
```

```{r check-destination-safe-worker-responses}
data_exit |>
    dplyr::filter(is_hoh_and_or_adult == "Yes") |>
    create_data_quality_table(
        response_column = "destination_safe_worker",
        no_response_values = c("Worker does not know", "Data not collected"),
        total_label = "Total Heads of Household and/or Adults Exits",
        table_title = "Destination Safe Worker (Exit)"
    )
```
